Notes on Prediction Types

### 2011-06-21 docs/pert_notes/pert.tex
predict_rhoX -> predict_rhoprime_and_rhoX

\begin{table}[h]
\centering
\caption{Summary of species edge state construction}
\label{table:pred:species}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|c|c}
\hline
\hline
{\tt species\_pred\_type} &   {quantities predicted} & {$(\rho X_k)$ edge state} \\[-5pt]
 & {in {\tt make\_edge\_scal}} & \\
\hline 
1 / {\tt predict\_rhoprime\_and\_X}  &  
  $\rho'_\mathrm{edge}$, $(X_k)_\mathrm{edge}$ &
  $\left(\rho_0^{n+\myhalf,{\rm avg}}  
  + \rho'_\mathrm{edge} \right)(X_k)_\mathrm{edge}$ \\
2 / {\tt predict\_rhoX}  &  
  $\rho'_\mathrm{edge}$, $(\rho X_k)_\mathrm{edge}$ &
  $(\rho X_k)_\mathrm{edge}$ \\
3 / {\tt predict\_rho\_and\_X}  &  
  $\rho_\mathrm{edge}$, $(X_k)_\mathrm{edge}$ &
  $\rho_\mathrm{edge} (X_k)_\mathrm{edge}$ \\
\hline
\end{tabular}
\end{table}
We note the labels {\tt predict\_rhoprime\_and\_X}, {\tt predict\_rhoX}, and
{\tt predict\_rho\_and\_X} are provided by the {\tt pred\_parameters}
module.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt species\_pred\_type} = {\tt predict\_rhoX}}

@@

\noindent {\tt species\_pred\_type = predict\_rhoX}:
\begin{equation}
\frac{\partial\rho X_k}{\partial t} = 
-\nabla\cdot\left\{\left[\left(\rho X_k \right)_\mathrm{edge} \right](\Ubt+w_0\eb_r)\right\}.
\end{equation}

@@

\begin{landscape}
\begin{table}[t]
\caption{Summary of enthalpy edge state construction}
\label{table:pred:hoverview}
\renewcommand{\arraystretch}{1.5}
{\small
\centering
\begin{tabular}{l|l|c|c|c|c}
\hline
\hline
{\tt species\_pred\_type} &   
{\tt enthalpy\_pred\_type} &
{cell-centered} &
{intermediate} &
{species quantity} &
{final $(\rho h)$} \\[-5pt]
 &
 &
{quantity predicted} &
{``enthalpy''} &
{available in {\tt mkflux}} &
{edge state} \\[-5pt]
 &
 &
{in {\tt make\_edge\_scal}} &
{edge state} &
 &
 \\
\hline 
1 / {\tt predict\_rhoprime\_and\_X}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
\hline
\hline
2 / {\tt predict\_rhoX}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
2 / {\tt predict\_rhoX}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
2 / {\tt predict\_rhoX}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
2 / {\tt predict\_rhoX}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
\hline
\end{tabular}
} % end \small
\end{table}
\end{landscape}

@@

\begin{table*}[h]
\centering
\caption{EOS states in {\tt makeHfromRhoT\_edge}\newline}
\label{table:pred:EOSinputs}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|c|c}
\hline
\hline
{\tt species\_pred\_type} & {$\rho$ edge state} &   {$X_k$ edge state}  \\
\hline
{\tt predict\_rhoprime\_and\_X} & 
  $\rho_0^{n+\myhalf,\rm{avg}} + \rho'_\mathrm{edge}$ & 
  $(X_k)_\mathrm{edge}$ \\
{\tt predict\_rhoX} & 
  $\sum_k (\rho X_k)_\mathrm{edge}$ & 
  $(\rho X_k)_\mathrm{edge}/\sum_k (\rho X_k)_\mathrm{edge}$ \\
\hline
\end{tabular}
\end{table*}

>>>>

\begin{table}[h]
\centering
\caption{Summary of species edge state construction}
\label{table:pred:species}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|c|c}
\hline
\hline
{\tt species\_pred\_type} &   {quantities predicted} & {$(\rho X_k)$ edge state} \\[-5pt]
 & {in {\tt make\_edge\_scal}} & \\
\hline 
1 / {\tt predict\_rhoprime\_and\_X}  &  
  $\rho'_\mathrm{edge}$, $(X_k)_\mathrm{edge}$ &
  $\left(\rho_0^{n+\myhalf,{\rm avg}}  
  + \rho'_\mathrm{edge} \right)(X_k)_\mathrm{edge}$ \\
2 / {\tt predict\_rhoprime\_and\_rhoX}  &  
  $\rho'_\mathrm{edge}$, $(\rho X_k)_\mathrm{edge}$ &
  $(\rho X_k)_\mathrm{edge}$ \\
3 / {\tt predict\_rho\_and\_X}  &  
  $\rho_\mathrm{edge}$, $(X_k)_\mathrm{edge}$ &
  $\rho_\mathrm{edge} (X_k)_\mathrm{edge}$ \\
\hline
\end{tabular}
\end{table}
We note the labels {\tt predict\_rhoprime\_and\_X}, {\tt predict\_rhoprime\_and\_rhoX}, and
{\tt predict\_rho\_and\_X} are provided by the {\tt pred\_parameters}
module.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt species\_pred\_type} = {\tt predict\_rhoprime\_and\_rhoX}}

@@

\noindent {\tt species\_pred\_type = predict\_rhoprime\_and\_rhoX}:
\begin{equation}
\frac{\partial\rho X_k}{\partial t} = 
-\nabla\cdot\left\{\left[\left(\rho X_k \right)_\mathrm{edge} \right](\Ubt+w_0\eb_r)\right\}.
\end{equation}

@@

\begin{landscape}
\begin{table}[t]
\caption{Summary of enthalpy edge state construction}
\label{table:pred:hoverview}
\renewcommand{\arraystretch}{1.5}
{\small
\centering
\begin{tabular}{l|l|c|c|c|c}
\hline
\hline
{\tt species\_pred\_type} &   
{\tt enthalpy\_pred\_type} &
{cell-centered} &
{intermediate} &
{species quantity} &
{final $(\rho h)$} \\[-5pt]
 &
 &
{quantity predicted} &
{``enthalpy''} &
{available in} &
{edge state} \\[-5pt]
 &
 &
{in {\tt make\_edge\_scal}} &
{edge state} &
{\tt mkflux} &
 \\
\hline 
1 / {\tt predict\_rhoprime\_and\_X}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
\hline
\hline
2 / {\tt predict\_rhoprime\_and\_rhoX}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
2 / {\tt predict\_rhoprime\_and\_rhoX}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
2 / {\tt predict\_rhoprime\_and\_rhoX}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
2 / {\tt predict\_rhoprime\_and\_rhoX}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
\hline
\end{tabular}
} % end \small
\end{table}
\end{landscape}

@@

\begin{table*}[h]
\centering
\caption{EOS states in {\tt makeHfromRhoT\_edge}\newline}
\label{table:pred:EOSinputs}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|c|c}
\hline
\hline
{\tt species\_pred\_type} & {$\rho$ edge state} &   {$X_k$ edge state}  \\
\hline
{\tt predict\_rhoprime\_and\_X} & 
  $\rho_0^{n+\myhalf,\rm{avg}} + \rho'_\mathrm{edge}$ & 
  $(X_k)_\mathrm{edge}$ \\
{\tt predict\_rhoprime\_and\_rhoX} & 
  $\sum_k (\rho X_k)_\mathrm{edge}$ & 
  $(\rho X_k)_\mathrm{edge}/\sum_k (\rho X_k)_\mathrm{edge}$ \\
\hline
\end{tabular}
\end{table*}
